### 2012-02-12 exam3/1.tex
First crack at problem 1.

A \emph{range} represents a set of numbers between two endpoints.  To
start with, you only need to consider ranges that \emph{include} the
smaller endpoint and \emph{exclude} the larger endpoint---such ranges
are called \emph{half-open}.  For example, the range $[3,4.7)$
includes all of the numbers between $3$ and $4.7$, including $3$ but
\emph{not} including $4.7$. So $4$ and $3.0000001$ are both in the
range, but $5$ is not.  In the notation used here, the $[$ means
include, and the $)$ means exclude.

\smallskip

\noindent
\begin{enumerate}
\item Design a representation for ranges and implement the
  \texttt{in-range?} method, which determines if a number is in the
  range.  For example, the range $[3,7.2)$ includes the numbers $3$
  and $5.0137$, but not the numbers $-17$ or $7.2$.

\item Extend the data definition and implementation of ranges to
  represent ranges that \emph{exclude} the low end of the range and
  \emph{include} the high end, written $(lo,hi]$.

\item Add a \texttt{union} method to the interface for ranges and
  implement it in all range classes.  This method should consume a
  range and produces a new range that includes all the numbers in this
  range \emph{and} all the numbers in the given range.

  You may extend your data definition for ranges to
  support this method.

  You may apply the abstraction recipe, but you are not required to do
  so; you will not be marked down for duplicated code on this problem.
\end{enumerate}

@@

\begin{solution}
\begin{verbatim}
;; Part 1:

;; A Range is one of
;; - (new range% Number Number)                         [1pt]
;; Interp: represents the range between `lo' and `hi'
;;         including `lo', but *not* including `hi'
;; and implements IRange:

;; The IRange interface includes:
;; - in-range? : Number -> Boolean                      [1pt]
;; determine if the given number is in this range
;; - union : Range -> Range                             [1pt]
;; produce the range containing this and the given range

(define-class range%                                    [1pt]
  (fields lo hi)
  (check-expect ((range% 0 1) . in-range? 0) true)      [1pt]
  (check-expect ((range% 0 1) . in-range? 1) false)
  (define/public (in-range? n)                          [2pt]
    (and (>= n (field lo)) (< n (field hi))))

  (define/public (union r)
    (union-range% this r)))

;; A Range is also:
;; - (new hi-range% Number Number)                      [1pt]
;; Interp: represents the range between `lo' and `hi'
;;         including `hi', but *not* including `lo'

(define-class hi-range%                                 [1pt]
  (fields lo hi)
  (check-expect ((hi-range% 0 1) . in-range? 0) false)  [1pt]
  (check-expect ((hi-range% 0 1) . in-range? 0.5) true)
  (check-expect ((hi-range% 0 1) . in-range? 1) true)
  (define/public (in-range? n)                          [1pt]
    (and (> n (field lo)) (<= n (field hi))))

  (define/public (union r)
    (union-range% this r)))

;; Part 3:

;; A Range is also:
;; - (new union-range% Range Range)                     [1pt]
;; Interp: including all the numbers in both ranges

(define-class union-range%                              [1pt]
  (fields left right)
  (define/public (in-range? n)                          [2pt]
    (or ((field left) . in-range? n)
        ((field right) . in-range? n)))

  ;; Point is for all the union methods together
  (define/public (union r)                              [1pt]
    (union-range% this r)))

(define r1 (range% 0 1))
(define r2 (hi-range% 0 1))
(define r3 (range% 2 4))

;; union + in-range? test                               [1pt]
(check-expect (r1 . union r2 . union r3 . in-range? 3) 
              true)

;; testing all the union methods                        [1pt]
(check-expect (r1 . union r2 . in-range? 1) true)
(check-expect (r2 . union r1 . in-range? 0) true)
\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

It will be helpful to define the helper methods \verb|add1| and
\verb|plus|.  Also, remember that $n + m = (n-1) + m + 1$ and that $n
\cdot m = (n-1) \cdot m + n$.

>>>>

Here is a data definition for a class of objects.  It intentionally
uses meaningless names to test whether you've sufficiently
internalized the data-driven development process we've talked about
since the Fall.

\begin{verbatim}
;; A P is one of:          
;; - A                  ;; An A is a (new a% String)
;; - B                  ;; A  B is a (new b% String A)
;; - C                  ;; A  C is a (new c% P)

(define-class a% (fields cookoo))
(define-class b% (fields gaga bang))
(define-class c% (fields doodle))
\end{verbatim}

\noindent
Design the following methods for \verb|P|s:

\begin{enumerate}

\item \verb|size| - the size of an \verb|A| is $5$; the size of a
  \verb|B| is $8$, regardless of what's inside; and the size of a
  \verb|C| contributes $1$ to the size of the \verb|P| inside.

\item \verb|replace-gaga| - produces a \verb|P| with the \verb|gaga|
  field of any \verb|B| within this \verb|P| with a given string.

\item \verb|same-gaga-cookoo?| - produces true for any \verb|P| which
  contains a \verb|B| whose \verb|gaga| is equal to a given string and
  whose \verb|bang| is an \verb|A| whose \verb|cookoo| is equal to
  another given string.  Produces false otherwise.

\end{enumerate}

Be sure to define any interfaces you need so that your program and say
which classes implement which interfaces so that your program treats
all values according to their interface.

@@

;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-gaga : String -> P
;;   Replace gaga field (if any) of this P with given string.
;; - same-gaga-cookoo? : String String -> Boolean
;;   Is there a B within this P with given gaga field and cookoo field?

;; An A implements:
;; - cookoo : -> String
;;   Get the cookoo string.

;; In a%:
(define (size) 5)
(define (replace-gaga str) this)
(define (same-gaga-cookoo? g c) false)

;; In b%:
(define (size) 8)
(define (replace-gaga str)
  (new b% str (this . bang)))
(define (same-gaga-cookoo? g c)
  (and (string=? g (this . gaga))
       (string=? c (this . bang . cookoo))))

;; In c%:
(define (size) (add1 (this . doodle . size)))
(define (replace-gaga str)
  (new c% (this . doodle . replace-gaga str)))
(define (same-gaga-cookoo? g c)
  (this . doodle . same-gaga-cookoo? g c))

\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

It will be helpful to define the helper methods \verb|add1| and
\verb|plus|.  Also, remember that $n + m = (n-1) + m + 1$ and that $n
\cdot m = (n-1) \cdot m + n$.  Don't overlook the slightly weird
specification for \verb|sub1|: $0-1 = 0$; this weirdness is common
amongst mathematicians when working with natural numbers.
